### 2024-04-23 texts/paper_closing.tex
add table of self-ID examples

Two measures are constructed that aim to capture an effect of legitimacy on closing.
First, self-identification measures whether a the name of a museum includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent).
Since the name is one of the first aspects that stakeholders perceive when engaging with an organization, it might very well shape expectations and influence forms of engagement.
In particular, it might be that museums that also refer to themselves as museums are seen as more favorable and worthy of visits, collaborations and support than other museums.

>>>>

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Tue Apr 23 17:09:15 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrll}
  \hline 
 \multicolumn{1}{l}{Self-identification} & \multicolumn{1}{l}{N} & \multicolumn{1}{l}{Self-ID (recoded)} & \multicolumn{1}{l}{examples}\\ 
 \hline
 Museum & 177 & Museum & Museum Kampa, Museum Barberini \\ 
  Foundation & 101 & Foundation & Marciano Art Foundation, Hill Art Foundation \\ 
  Collection &  74 & Collection & The Farjam Collection, Sammlung Boros \\ 
  None &  56 & Other & The Bunker, The Broad \\ 
  Center &  17 & Other & Dairy Art Centre, Art Center Nabi \\ 
  Art space &  12 & Other & El Espacio 23, Qiao Space \\ 
  Gallery &  11 & Other & Saatchi Gallery, Galerie C15 \\ 
  House / villa &  10 & Other & Villa La Fleur, Casa Daros Rio \\ 
  Institute &   9 & Other & Instituto Inhotim, Woods Art Institute \\ 
  Kunsthalle &   7 & Other & Kunsthalle Würth, G2 Kunsthalle \\ 
  Park / garden &   4 & Other & Schlosspark Eyebesfeld, Il Giardino dei Lauri \\ 
   \hline
\end{tabular}
\caption{Selfidentification} 
\label{tbl:t_selfid}
\end{table}

Two measures are constructed that aim to capture an effect of legitimacy on closing.
First, self-identification measures whether a the name of a museum includes the term "Museum", "Foundation", "Collection", or other (such as "Villa", "Institute", "Center" or "Gallery", which are grouped together as they are less frequent, see table \ref{tbl:t_selfid}).
Since the name is one of the first aspects that stakeholders perceive when engaging with an organization, it might very well shape expectations and influence forms of engagement.
In particular, it might be that museums that also refer to themselves as museums are seen as more favorable and worthy of visits, collaborations and support than other museums.
